The ChEMBL database as Linked Open Data

### 2012-04-15 article.tex
OK, no clue what further discussion to write up

While we show here that the triple version of the ChEMBL data is very useful, the current triples are by no means static: ChEMBL-RDF
will keep evolve, following new developments in the Linked Open Data world. For example, it is likely that over time we will link out
to more Linked Data resources. More importantly, we wish to adopt more ontologies, of which the BioAssay Ontology is planned
next~\cite{Visser2011}.

@@

Tim Hodson and Zach Beauvais of Kasabi for their support. What S.H. Name of the Bioinformatics department at Uppsala University.

>>>>

While we show here that the triple version of the ChEMBL data is very useful, the current triples are by no means static: ChEMBL-RDF
will keep evolve, following new developments in the Linked Open Data world. For example, it is likely that over time we will link out
to more Linked Data resources. More importantly, we wish to adopt more common ontologies, of which the BioAssay Ontology is planned
to be the first next to be adopted~\cite{Visser2011}. This should make the ChEMBL-RDF triples even more interoperable.

@@

Tim Hodson and Zach Beauvais of Kasabi and A. L\"ovgren at the at Uppsala Biomedical Centre at Uppsala University for their
support.
